Abstract Data Type Inference

### 2015-03-24 matching.tex
Quick typo fix.

  Consider again the language $L_\mathrm{reg}$ of read and write methods of
  Example~\ref{ex:register-language}, yet this time without the predicate ${\sf
  v}(e,o_1,o_2)$. The following table lists all possible predicate valuations
  $\tup{x_{\sf w}, y_{\sf w}}$, and for each valuation a valid execution which
  excludes the positive valuation of ${\sf g}(x_{\sf w}, y_{\sf w})$ in the
  satisfaction of $\textsc{Normalize}_F$.
  \begin{center}
    \begin{tabular}{cc|ll}
      $x_{\sf w}$ & $y_{\sf w}$ & counterexample & reason \\
      \hline
      0 & 0 & ${\rm w}(1)\ {\rm r}(1)\ {\rm r}(1)$ & not unique \\
      0 & 1 & $\underline{{\rm w}(1)\ {\rm r}(1)}\ {\rm r}(1)$ & $\to_\mathrm{m}$ \\
      1 & 0 & ${\rm w}(1)\ {\rm w}(2)\ {\rm r}(2)$ & not unique \\
      1 & 1 & ${\rm w}(1)\ {\rm w}(2)$ & not unique \\
    \end{tabular}
  \end{center}
  Thus any enumeration $F$ including the executions above excludes every
  possible valuation of $\tup{x_{\sf w}, y_{\sf w}}$, resulting in an
  unsatisfiable $\textsc{Normalize}_F$.

>>>>

  Consider again the language $L_\mathrm{reg}$ of read and write methods of
  Example~\ref{ex:register-language}, yet this time without the predicate ${\sf
  v}(e,o_1,o_2)$. The following table lists all possible predicate valuations
  $\tup{x_{\sf w}, y_{\sf w}}$, and for each valuation a valid execution which
  excludes the positive valuation of ${\sf g}(x_{\sf w}, y_{\sf w})$ in the
  satisfaction of $\textsc{Normalize}_F$.
  \begin{center}
    \begin{tabular}{cc|ll}
      $x_{\sf w}$ & $y_{\sf w}$ & counterexample & reason \\
      \hline
      $0$ & $0$ & ${\rm w}(1)\ {\rm r}(1)\ {\rm r}(1)$ & not unique \\
      $0$ & $1$ & $\underline{{\rm w}(1)\ {\rm r}(1)}\ {\rm r}(1)$ & $\to_\mathrm{m}$ \\
      $1$ & $0$ & ${\rm w}(1)\ {\rm w}(2)\ {\rm r}(2)$ & not unique \\
      $1$ & $1$ & ${\rm w}(1)\ {\rm w}(2)$ & not unique \\
    \end{tabular}
  \end{center}
  Thus any enumeration $F$ including the executions above excludes every
  possible valuation of $\tup{x_{\sf w}, y_{\sf w}}$, resulting in an
  unsatisfiable $\textsc{Normalize}_F$.
